Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-28 Paper/MSRChallenge2017.tex
added the NSF GRFP acknowledgement text
fixed a weird comma

We find that social factors are an important aspect of build success ,
do not fully predict whether a contribution will 
pass all build tests;
that core team members are more likely to achieve build success than non-core
members; and that developers with more followers are more likely to submit commits that pass the
continuous integration build.

@@

% use section* for acknowledgement
\section*{Acknowledgments}

The authors gratefully acknowledge the partial support
of the AFRL (AFRL Contract No. FA8750-15-2-0075). Any 
findings or recommendations are those of the author(s) and do not
necessarily reflect the views of the sponsoring agencies.

>>>>

We find that social factors are an important aspect of build success,
do not fully predict whether a contribution will 
pass all build tests;
that core team members are more likely to achieve build success than non-core
members; and that developers with more followers are more likely to submit commits that pass the
continuous integration build.

@@

% use section* for acknowledgement
\section*{Acknowledgments}
This material is based upon work supported by the National Science Foundation
Graduate Research Fellowship under Grant No. DGE-1252522.
The authors gratefully acknowledge the partial support
of the AFRL (AFRL Contract No. FA8750-15-2-0075). Any 
findings or recommendations are those of the author(s) and do not
necessarily reflect the views of the sponsoring agencies.
